A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-06-04 manuscript.Rmd
extend git introduction

First, to resolve ambiguity across multiple versions of code and data that may be come into existence during the development phase of a research project, we recommend the use of a version control system.
A version control system tracks changes to all project-related files (e.g., materials, data, and code) over time.
At a later stage, single files or the entire project can be compared to or reverted to an earlier version.
Additional features, such as branches, facilitate collaboration.
Specific snapshots of a repository can be marked, such that one can clearly label a given project status as the one that created a given preregistration, a given preprint, or the final authors' version accepted at a journal.
Using version control protects against loss of files and also supports remote collaboration with semi-automated tools for tracking and merging changes.

@@

Dynamic document generation fuses both steps and can be traced back to @knuthCWEBSystemStructured who put it this way: "The main idea is to regard a program as a communication to human beings rather than as a set of instructions to a computer."
This paradigm has gained popularity with the Sweave approach [@leisch2002sweave] that allowed embedding the data analysis into a TeX document, which then could be dynamically rendered into a final manuscript.
As of recently, R Markdown has added to the success of this idea.
R Markdown uses Markdown for writing the text, and R (or other programming languages) for the analysis. Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX), works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks (in fact, arbitrary computer code; see @riedererChapter15Other) into a Markdown document.
Upon rendering of the document, the code blocks are executed and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).

@@

simulation_results.csv: simulate.R
  Rscript -e 'source("simulate.R")'
```
There are two targets, the final rendered report (`manuscript.pdf`, l.1) and the simulation results (`simulation_results.csv`, l.4).
Each target is followed by a colon and a list of requirements.
If a requirement is  newer than the target, the recipe will be executed to rebuild the target.
If a requirement does not exist, Make seeks to find a recipe to build the requirement first before building the target.
Here, if one were to build the final `manuscript.pdf` by rendering the R Markdown with the command shown in l.2, Make would make sure that the file `simulation_results.csv` exists; if not, it would find that this is also a target and issue the command in l.5 to run the simulation first before rendering the manuscript.
This way, we ensure that the simulation is always run before the manuscript is built and that the manuscript is rebuilt if the simulation code was changed.

>>>>

First, to resolve ambiguity across multiple versions of code and data that may be come into existence during the development phase of a research project, we recommend the use of a version control system.
Version control allows a clear link between which results were generated by which verion of code and data.

A version control system tracks changes to all project-related files (e.g., materials, data, and code) over time.
At a later stage, single files or the entire project can be compared to or reverted to an earlier version.
A version controlled project is makes the loss of files unlikely and also supports remote collaboration.

We recommend to use Git for version control, because of its widespread adoption in the R community.
Git is build around snapshots which represent the entire project state at a given point in time.
Those snapshots are called "commits".
Each file that was changed has to be added to a commit and each commit requires a commit message that succinctly describes the changes made.
Each commit "knows" its ancestor and they build a timeline together.
The conglomerate of commits (i.e. the version controlled project) is called repository.
In Git specific snapshots of a repository can be tagged, such that one can clearly label a given project status as the one that created a given preregistration, a given preprint, or the final authors' version accepted at a journal.
Git has additional features beyond basic version control, such as branches to facilitate collaboration.
To collaborate on a Git repository, the repository has to be uploaded somewhere.
We recommend GitHub to host Git repositories because of its popularity among R users.
GitHub has many tools that ease project management and collaboration and these tools provide much value in our everyday work but they are not central to archiving reproducibility.

@@

Dynamic document generation fuses both steps and can be traced back to @knuthCWEBSystemStructured who put it this way: "The main idea is to regard a program as a communication to human beings rather than as a set of instructions to a computer."
R Markdown uses Markdown for writing the text, and R (or other programming languages) for the analysis. Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX), works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks (in fact, arbitrary computer code; see @riedererChapter15Other) into a Markdown document.
Upon rendering of the document, the code blocks are executed and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).

@@

simulation_results.csv: simulate.R
  Rscript -e 'source("simulate.R")'
```

There are two targets, the final rendered report (`manuscript.pdf`, l.1) and the simulation results (`simulation_results.csv`, l.4).
Each target is followed by a colon and a list of requirements.
If a requirement is  newer than the target, the recipe will be executed to rebuild the target.
If a requirement does not exist, Make seeks to find a recipe to build the requirement first before building the target.
Here, if one were to build the final `manuscript.pdf` by rendering the R Markdown with the command shown in l.2, Make would make sure that the file `simulation_results.csv` exists; if not, it would find that this is also a target and issue the command in l.5 to run the simulation first before rendering the manuscript.
This way, we ensure that the simulation is always run before the manuscript is built and that the manuscript is rebuilt if the simulation code was changed.
